Our Title

### 2015-05-01 draft.tex
Added in a note for a missing reference.

As ISIL carving its traction in Iraq and Syria, the two countries become an immediate concern for help by the U.S.. Strengthening Iraq and Syria could be among the first line of defense against ISIL. As U.S. has an improving bilateral relations with Iraq, Iraq become an easier partner for U.S. to work with in reigning ISIL. The Strategic Framework Agreement for a Relationship of Friendship and Cooperation between the U.S. and the Republic of Iraq guides the overall political, economic, cultural, and security ties with Iraq.  This agreement is designed to help the Iraqi people stand on their own and reinforce Iraqi sovereignty, while protecting U.S. interests in the Middle East.

@@

The Information Security Oversight Office (ISOO) determines standards for information classification based on policy guidance from the National Security Council (NSC). ISOO has oversight of the extensive security characterization framework and the National Industrial Security Program. ISOO sets requirements for the original classification of information if the following apply: information should be classified by the classification authority; information is belongs to, controlled by, or is for the United States; information refers to one of the classification categories; classification authorities determines damage will be caused to national security from unsanctioned disclosure [10]. The classes of information classification believed to be effective \cite{Richelson2011}.  The general classes of classification are:

>>>>

As ISIL carves its traction in Iraq and Syria, the two countries become an immediate concern for help by the U.S.. Strengthening Iraq and Syria could be among the first line of defense against ISIL. As U.S. has an improving bilateral relations with Iraq, Iraq become an easier partner for U.S. to work with in reigning ISIL. The Strategic Framework Agreement for a Relationship of Friendship and Cooperation between the U.S. and the Republic of Iraq guides the overall political, economic, cultural, and security ties with Iraq.  This agreement is designed to help the Iraqi people stand on their own and reinforce Iraqi sovereignty, while protecting U.S. interests in the Middle East.

@@

\subsection{??????? Add in Ref 10 below from Bushra  ???????}

The Information Security Oversight Office (ISOO) determines standards for information classification based on policy guidance from the National Security Council (NSC). ISOO has oversight of the extensive security characterization framework and the National Industrial Security Program. ISOO sets requirements for the original classification of information if the following apply: information should be classified by the classification authority; information is belongs to, controlled by, or is for the United States; information refers to one of the classification categories; classification authorities determines damage will be caused to national security from unsanctioned disclosure [10]. The classes of information classification believed to be effective \cite{Richelson2011}, [10].  The general classes of classification are:

10 Federal Register. "The President”, Part VII 75, 2010
